Results

### 2023-02-24 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
found p values of model

The second model explained `r papaja::printnum(MLM2_r2[2])` percent of variance.

``` {r TabMLM_H5, echo=FALSE, message=FALSE, warning=FALSE}
papaja::apa_table(
  H5_M2_table,
  caption = "Results of multilevel model predicting subjective values of ER strategies.",
  escape = FALSE,
  placement = "H")
```

>>>>

The second model explained `r papaja::printnum(MLM2_r2[2])` percent of variance. 
All results of the second model are in table\ \@ref(tab:TabMLM_H5).

``` {r TabMLM_H5, echo=FALSE, message=FALSE, warning=FALSE}
papaja::apa_table(
  H5_M2_table,
  caption = "Results of multilevel model predicting subjective values of ER strategies.",
  booktabs = TRUE,
  escape = FALSE,
  placement = "H")
```

The predictors effort ($p=$ `r papaja::printnum(summary(MLM_2)$coefficients[1,5])`), ...
